\section{Background}
\label{sec:background}


\noindent{\textbf{Distributed Snapshot}} is an algorithm which
proposes that consistent distributed state can be captured without
interfering with the execution of a system itself
~\cite{dist_snapshots_Chandy1985}.  Distributed snapshots can be
computed online or mined from a log containing vector clocks which
provide a partial ordering of events in a
system~\cite{mattern_vector_clocks_1989}. We consider distributed
snapshots to be a fundamental granularity for examining consistent
state. Our state analysis technique is therefore applied at the level
of a distributed snapshot.

\noindent{\textbf{\dinv}} is a tool which detects likely data invariants in distributed
systems~\cite{dinv}. \dinv operates by instrumenting distributed
systems to log state and vector clocks. Execution logs from the nodes
of the system are merged together, and the state of the system is
reconstructed and output as a distributed system trace. \dinv
leverages Daikon to automatically infer data invariants on the trace.
We plan to use \dinv as a tool for capturing distributed state.

\noindent{\textbf{Visualization}} is useful for helping users
comprehend complicated data.  Understanding distributed systems is a
challenging task for system designers, software developers and
students because of their inherent complexity.  Prior work on the
visualization on system traces has demonstrated that similarities in
the traces between software versions can be meaningfully conveyed to
developers~\cite{6613833}. Alternative work has demonstrated that
visualizing concurrent system traces using partial orderings can help
developers reason about interleaving
executions~\cite{6650534}~\cite{7272586}. We consider the state of a
system to be a direct artifact of a system trace. To our knowledge no
attempts have been made to visualize distributed system traces, and by
extension distributed state traces.

%There are a few studies focusing on 
%performance diagnositics of parallel or distributed systems, but few are done
%to understand the distributed nature in terms of state machines: 
%how distributed states transit.
%Visualization is suitable when there is enough data but no automatic algorithms
%to dig out the insights that people are looking for.  Here we can generate logs
%that we need by \textbf{TODO}, and there does not exist a general model that 
%can capture the distributed nature.

%\begin{itemize}
%\item modular visualization of distributed systems
%\item pip \textit{http://issg.cs.duke.edu/pip/}
%\item Overview: A Framework for Generic Online Visualization of Distributed
%Systems
%\item Jumpshot \textit{http://www.mcs.anl.gov/research/projects/perfvis/software/viewers/}
%\item vampire: http://citeseer.ist.psu.edu/viewdoc/summary?doi=10.1.1.38.1615
%\end{itemize}
